---
title: "Clean"
author: "Joshua Berry"
date: "11/12/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(foreign)
library(haven)
library(tidyverse)
```

## R Markdown

use huxtable to make tables piping in from stan_glm
https://cran.r-project.org/web/packages/huxtable/vignettes/huxtable.html
https://hughjonesd.github.io/huxtable/

Does attitudes towards China vary with amount of trade? So do countries that
trade more with China lead to more negative/positive attitudes towards China?


input: trade with China as a percentage of GDP... aka interaction with China

output: favoribility towards China by country

Clean up datasets, merge by country, trade as percentage of GDP


```{r}

pew_2019 <- 
read_sav("Pew Research Center Global Attitudes Spring 2019 Dataset WEB.sav") %>%
  as_factor() %>%
  filter(country %in% c("Argentina", "Australia", "Brazil", "Canada", "France",
                      "Germany", "India", "Indonesia", "Italy", "Japan",
                      "Mexico", "Russia", "South Africa", "South Korea",
                      "Turkey", "United Kingdom", "United States")) %>%
  select(country, COUNTRY_SATIS, ECON_SIT, CHILDREN_BETTEROFF2, 
         SATISFIED_DEMOCRACY, FAV_US, FAV_CHINA, ECON_POWER, CHINA_INFLU_ECON2,
         USE_INTERNET, SOCIAL_NET, SEX, AGE, POLITICAL_SCALE2, D_DENSITY) %>%
  rename(COUNTRY = country, country_satis = COUNTRY_SATIS, econ_sit = ECON_SIT,
         children_betteroff2 = CHILDREN_BETTEROFF2, 
         satisfied_democracy = SATISFIED_DEMOCRACY, fav_US = FAV_US, 
         fav_China = FAV_CHINA, econ_power = ECON_POWER,
         use_internet = USE_INTERNET, social_net = SOCIAL_NET, 
         sex = SEX, age = AGE, political_scale2 = POLITICAL_SCALE2, 
         d_density = D_DENSITY)

pew_2018 <- 
read_sav("Pew Research Global Attitudes Spring 2018 Dataset WEB FINAL.sav") %>%
  as_factor() %>%
  filter(COUNTRY %in% c("Argentina", "Australia", "Brazil", "Canada", "France",
                      "Germany", "India", "Indonesia", "Italy", "Japan",
                      "Mexico", "Russia", "South Africa", "South Korea",
                       "United Kingdom", "United States")) %>%
  select(COUNTRY, country_satis, econ_sit, children_betteroff2, 
         satisfied_democracy, fav_US, fav_China, econ_power,
         use_internet, social_net, sex, age, d_density)

pew_2017 <- 
read_sav("Pew Research Global Attitudes Spring 2017 Dataset WEB FINAL.sav") %>%
  as_factor() %>%
  filter(Country %in% c("Argentina", "Australia", "Brazil", "Canada", "France",
                      "Germany", "India", "Indonesia", "Italy", "Japan",
                      "Mexico", "Russia", "South Africa", "South Korea",
                       "Turkey", "United Kingdom", "United States")) %>%
  select(Country, country_satis, econ_sit, children_betteroff2, 
         satisfied_democracy, fav_US, fav_China, econ_power,
         use_internet, social_net, sex, age, political_scale2, d_density) %>% rename(COUNTRY = country)

pew_2016 <- 
read_sav("Pew Research Center Spring 2016 Global Attitudes.sav") %>%
  as_factor() %>%
  filter(country %in% c("Argentina", "Australia", "Brazil", "Canada", "France",
                      "Germany", "India", "Indonesia", "Italy", "Japan",
                      "Mexico", "Russia", "South Africa", "South Korea",
                       "Turkey", "United Kingdom", "United States")) %>%
  select(country, q3, Q10A, Q10B, Q23,
         q79, q82, q107, q108) %>%
   rename(COUNTRY = country, country_satis = q3,
         fav_US = Q10A, fav_China = Q10B, econ_power = Q23,
         use_internet = q79, social_net = q82, sex = q107,
         age = q108)

pew_2015 <- 
read_sav("Pew Research Global Attitudes Spring 2015 FINAL.sav") %>%
  as_factor() %>%
  filter(COUNTRY %in% c("Argentina", "Australia", "Brazil", "Canada", "France",
                      "Germany", "India", "Indonesia", "Italy", "Japan",
                      "Mexico", "Russia", "South Africa", "South Korea",
                       "Turkey", "United Kingdom", "United States")) %>%
  select(COUNTRY, Q2, Q3, Q12A, Q12B, Q17,
         Q70, Q74, Q145, Q146) %>%
   rename(country_satis = Q2, econ_sit = Q3,
         fav_US = Q12A, fav_China = Q12B, econ_power = Q17,
         use_internet = Q70, social_net = Q74, sex = Q145,
         age = Q146)

pew_2014 <- 
read_sav("Pew Research Global Attitudes Spring 2014.sav") %>%
  as_factor() %>%
  filter(COUNTRY %in% c("Argentina", "Australia", "Brazil", "Canada", "France",
                      "Germany", "India", "Indonesia", "Italy", "Japan",
                      "Mexico", "Russia", "South Africa", "South Korea",
                       "Turkey", "United Kingdom", "United States")) %>%
  select(COUNTRY, Q5, Q9, Q11, Q15A, Q15B, Q33,
         Q67, Q72, Q132, Q133) %>%
  rename(country_satis = Q5, econ_sit = Q9, children_betteroff2 = Q11,
         fav_US = Q15A, fav_China = Q15B, econ_power = Q33,
         use_internet = Q67, social_net = Q72, sex = Q132,
         age = Q133)

pew_2013 <- 
read_sav("Pew Research Global Attitudes Project Spring 2013.sav") %>%
  as_factor() %>%
  filter(COUNTRY %in% c("Argentina", "Australia", "Brazil", "Canada", "France",
                      "Germany", "India", "Indonesia", "Italy", "Japan",
                      "Mexico", "Russia", "South Africa", "South Korea",
                       "Turkey", "United Kingdom", "United States")) %>%
  select(COUNTRY, Q1, Q4, Q8, Q9A, Q9C, Q29,
         Q66, Q73, Q164, Q165) %>%
  rename(country_satis = Q1, econ_sit = Q4, children_betteroff2 = Q8,
         fav_US = Q9A, fav_China = Q9C, econ_power = Q29,
         use_internet = Q66, social_net = Q73, sex = Q164,
         age = Q165)

pew_2012 <- 
read_sav("Pew Research Global Attitudes Project Spring 2012.sav") %>%
  as_factor() %>%
  filter(COUNTRY %in% c("Argentina", "Australia", "Brazil", "Canada", "France",
                      "Germany", "India", "Indonesia", "Italy", "Japan",
                      "Mexico", "Russia", "South Africa", "South Korea",
                       "Turkey", "United Kingdom", "United States")) %>%
  select(COUNTRY, Q2, Q4, Q8A, Q8C, Q14, Q29,
         Q77, Q79, Q141, Q142) %>%
  rename(country_satis = Q2, econ_sit = Q14, children_betteroff2 = Q4,
         fav_US = Q8A, fav_China = Q8C, econ_power = Q29,
         use_internet = Q77, social_net = Q79, sex = Q141,
         age = Q142)

```


```{r}

cc_2019 <- read_sav("2019 Chicago Council Survey - Datafile.sav")

glimpse(pew_2019)

pew_2019_c <- pew_2019 %>%
  filter(country == "United States") %>%
  ggplot(aes(x = FAV_CHINA)) +
  geom_bar()
```

