---
title: "Clean"
author: "Joshua Berry"
date: "11/12/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(foreign)
library(haven)
library(tidyverse)
library(readxl)
library(memisc)
library(rstanarm)
library(ggridges)
library(gtsummary)
library(broom.mixed)
library(gt)
```

## R Markdown

use huxtable to make tables piping in from stan_glm
https://cran.r-project.org/web/packages/huxtable/vignettes/huxtable.html
https://hughjonesd.github.io/huxtable/

Does attitudes towards China vary with amount of trade? So do countries that
trade more with China lead to more negative/positive attitudes towards China?


input: trade with China as a percentage of GDP... aka interaction with China

output: favoribility towards China by country

Clean up datasets, merge by country, trade as percentage of GDP


```{r}

pew_2019 <- 
read_sav("Pew Research Center Global Attitudes Spring 2019 Dataset WEB.sav") %>%
  as_factor() %>%
  filter(country %in% c("Argentina", "Australia", "Brazil", "Canada", "France",
                      "Germany", "India", "Indonesia", "Italy", "Japan",
                      "Mexico", "Russia", "South Africa", "South Korea",
                      "Turkey", "United Kingdom", "United States")) %>%
  select(country, COUNTRY_SATIS, ECON_SIT, CHILDREN_BETTEROFF2, 
         SATISFIED_DEMOCRACY, FAV_US, FAV_CHINA, ECON_POWER, CHINA_INFLU_ECON2,
         USE_INTERNET, SOCIAL_NET, SEX, AGE, POLITICAL_SCALE2, D_DENSITY) %>%
  rename(COUNTRY = country, country_satis = COUNTRY_SATIS, econ_sit = ECON_SIT,
         children_betteroff = CHILDREN_BETTEROFF2, 
         satisfied_democracy = SATISFIED_DEMOCRACY, fav_US = FAV_US, 
         fav_China = FAV_CHINA, econ_power = ECON_POWER,
         use_internet = USE_INTERNET, social_net = SOCIAL_NET, 
         sex = SEX, age = AGE, political_scale2 = POLITICAL_SCALE2, 
         d_density = D_DENSITY) %>%
  mutate(year = 2019)

pew_2018 <- 
read_sav("Pew Research Global Attitudes Spring 2018 Dataset WEB FINAL.sav") %>%
  as_factor() %>%
  filter(COUNTRY %in% c("Argentina", "Australia", "Brazil", "Canada", "France",
                      "Germany", "India", "Indonesia", "Italy", "Japan",
                      "Mexico", "Russia", "South Africa", "South Korea",
                       "United Kingdom", "United States")) %>%
  select(COUNTRY, country_satis, econ_sit, children_betteroff2, 
         satisfied_democracy, fav_US, fav_China, econ_power,
         use_internet, social_net, sex, age, d_density)  %>%
  rename(children_better0ff = children_betteroff2) %>%
  mutate(year = 2018)

pew_2017 <- 
read_sav("Pew Research Global Attitudes Spring 2017 Dataset WEB FINAL.sav") %>%
  as_factor() %>%
  filter(Country %in% c("Argentina", "Australia", "Brazil", "Canada", "France",
                      "Germany", "India", "Indonesia", "Italy", "Japan",
                      "Mexico", "Russia", "South Africa", "South Korea",
                       "Turkey", "United Kingdom", "United States")) %>%
  select(Country, country_satis, econ_sit, children_betteroff2, 
         satisfied_democracy, fav_US, fav_China, econ_power,
         use_internet, social_net, sex, age, political_scale2, d_density) %>%
  rename(COUNTRY = Country, children_better0ff = children_betteroff2)  %>%
  mutate(year = 2017)

pew_2016 <- 
read_sav("Pew Research Center Spring 2016 Global Attitudes.sav") %>%
  as_factor() %>%
  filter(country %in% c("Argentina", "Australia", "Brazil", "Canada", "France",
                      "Germany", "India", "Indonesia", "Italy", "Japan",
                      "Mexico", "Russia", "South Africa", "South Korea",
                       "Turkey", "United Kingdom", "United States")) %>%
  select(country, q3, Q10A, Q10B, Q23,
         q79, q82, q107, q108) %>%
   rename(COUNTRY = country, country_satis = q3,
         fav_US = Q10A, fav_China = Q10B, econ_power = Q23,
         use_internet = q79, social_net = q82, sex = q107,
         age = q108)  %>%
  mutate(year = 2016)

pew_2015 <- 
read_sav("Pew Research Global Attitudes Spring 2015 FINAL.sav") %>%
  as_factor() %>%
  filter(COUNTRY %in% c("Argentina", "Australia", "Brazil", "Canada", "France",
                      "Germany", "India", "Indonesia", "Italy", "Japan",
                      "Mexico", "Russia", "South Africa", "South Korea",
                       "Turkey", "United Kingdom", "United States")) %>%
  select(COUNTRY, Q2, Q3, Q12A, Q12B, Q17,
         Q70, Q74, Q145, Q146) %>%
   rename(country_satis = Q2, econ_sit = Q3,
         fav_US = Q12A, fav_China = Q12B, econ_power = Q17,
         use_internet = Q70, social_net = Q74, sex = Q145,
         age = Q146)  %>%
  mutate(year = 2015)

pew_2014 <- 
read_sav("Pew Research Global Attitudes Spring 2014.sav") %>%
  as_factor() %>%
  filter(COUNTRY %in% c("Argentina", "Australia", "Brazil", "Canada", "France",
                      "Germany", "India", "Indonesia", "Italy", "Japan",
                      "Mexico", "Russia", "South Africa", "South Korea",
                       "Turkey", "United Kingdom", "United States")) %>%
  select(COUNTRY, Q5, Q9, Q11, Q15A, Q15B, Q33,
         Q67, Q72, Q132, Q133) %>%
  rename(country_satis = Q5, econ_sit = Q9, children_betteroff = Q11,
         fav_US = Q15A, fav_China = Q15B, econ_power = Q33,
         use_internet = Q67, social_net = Q72, sex = Q132,
         age = Q133)  %>%
  mutate(year = 2014)

pew_2013 <- 
read_sav("Pew Research Global Attitudes Project Spring 2013.sav") %>%
  as_factor() %>%
  filter(COUNTRY %in% c("Argentina", "Australia", "Brazil", "Canada", "France",
                      "Germany", "India", "Indonesia", "Italy", "Japan",
                      "Mexico", "Russia", "South Africa", "South Korea",
                       "Turkey", "United Kingdom", "United States")) %>%
  select(COUNTRY, Q1, Q4, Q8, Q9A, Q9C, Q29,
         Q66, Q73, Q164, Q165) %>%
  rename(country_satis = Q1, econ_sit = Q4, children_betteroff = Q8,
         fav_US = Q9A, fav_China = Q9C, econ_power = Q29,
         use_internet = Q66, social_net = Q73, sex = Q164,
         age = Q165)  %>%
  mutate(year = 2013)

pew_2012 <- 
read_sav("Pew Research Global Attitudes Project Spring 2012.sav") %>%
  as_factor() %>%
  filter(COUNTRY %in% c("Argentina", "Australia", "Brazil", "Canada", "France",
                      "Germany", "India", "Indonesia", "Italy", "Japan",
                      "Mexico", "Russia", "South Africa", "South Korea",
                       "Turkey", "United Kingdom", "United States")) %>%
  select(COUNTRY, Q2, Q4, Q8A, Q8C, Q14, Q29,
         Q77, Q79, Q141, Q142) %>%
  rename(country_satis = Q2, econ_sit = Q14, children_betteroff = Q4,
         fav_US = Q8A, fav_China = Q8C, econ_power = Q29,
         use_internet = Q77, social_net = Q79, sex = Q141,
         age = Q142)  %>%
  mutate(year = 2012)

pew_2011 <- 
read_sav("Pew Global Attitudes Spring 2011 Dataset WEB.sav") %>%
  as_factor() %>%
  filter(COUNTRY %in% c("Argentina", "Australia", "Brazil", "Canada", "France",
                      "Germany", "India", "Indonesia", "Italy", "Japan",
                      "Mexico", "Russia", "South Africa", "South Korea",
                       "Turkey", "United Kingdom", "United States")) %>%
 select(COUNTRY, Q2, Q4, Q3A, Q3C, Q26,
         Q66, Q69, Q111, Q112) %>%
  rename(country_satis = Q2, econ_sit = Q4,
         fav_US = Q3A, fav_China = Q3C, econ_power = Q26,
         use_internet = Q66, social_net = Q69, sex = Q111,
         age = Q112)  %>%
  mutate(year = 2011)

pew_2010 <- 
read_sav("Pew Global Attitudes Spring 2010 Dataset For Release.sav") %>%
  as_factor() %>%
  filter(COUNTRY %in% c("Argentina", "Australia", "Brazil", "Canada", "France",
                      "Germany", "India", "Indonesia", "Italy", "Japan",
                      "Mexico", "Russia", "South Africa", "South Korea",
                       "Turkey", "United Kingdom", "United States")) %>%
  select(COUNTRY, Q5, Q12, Q7A, Q7C, Q25,
         Q63, Q66, Q120, Q121) %>%
  rename(country_satis = Q5, econ_sit = Q12,
         fav_US = Q7A, fav_China = Q7C, econ_power = Q25,
         use_internet = Q63, social_net = Q66, sex = Q120,
         age = Q121)  %>%
  mutate(year = 2010)

pew_2009 <- 
  read.spss('Pew Gap 2009 Data.sav', to.data.frame=TRUE) %>%
  as_factor() %>%
  filter(COUNTRY %in% c("Argentina", "Australia", "Brazil", "Canada", "France",
                      "Germany", "India", "Indonesia", "Italy", "Japan",
                      "Mexico", "Russia", "South Africa", "South Korea",
                       "Turkey", "United Kingdom", "United States")) %>%
  select(COUNTRY, Q4, Q5, Q8, Q11A, Q11C, Q15,
         Q80, Q81) %>%
  rename(country_satis = Q4, econ_sit = Q5, children_betteroff = Q8,
         fav_US = Q11A, fav_China = Q11C, econ_power = Q15,
         sex = Q80, age = Q81)  %>%
  mutate(year = 2009)
```


```{r}

g20_gdp <- 
  read_csv("GDP_G20.csv") %>%
   filter(LOCATION %in% c("ARG", "AUS", "BRA", "CAN", "FRA",
                      "DEU", "IND", "IDN", "ITA", "JPN",
                      "MEX", "RUS", "ZAF", "KOR",
                       "TUR", "GBR", "USA")) %>%
  select(LOCATION, TIME, Value) %>%
  rename(COUNTRY = LOCATION, year = TIME, gdp_tot = Value) %>%
  mutate(COUNTRY = recode(COUNTRY,
                          "AUS" = "Australia",
                          "ARG" = "Argentina",
                          "BRA" = "Brazil",
                          "CAN" = "Canada",
                          "FRA" = "France",
                          "DEU" = "Germany",
                          "IND" = "India",
                          "IDN" = "Indonesia",
                          "ITA" = "Italy",
                          "JPN" = "Japan",
                          "MEX" = "Mexico",
                          "RUS" = "Russia",
                          "ZAF" = "South Africa",
                          "KOR" = "South Korea",
                          "TUR" = "Turkey",
                          "GBR" = "United Kingdom",
                          "USA" = "United States"))

china_imf_imports <-
  read_excel("Imports_China.xlsx", skip = 5) %>%
  pivot_longer(cols = - c(`...1`),
               names_to = "year") %>%
  rename(COUNTRY = `...1`, china_imports = value) %>%
   filter(COUNTRY %in% c("Argentina", "Australia", "Brazil", "Canada", "France",
                      "Germany", "India", "Indonesia", "Italy", "Japan",
                      "Mexico", "Russian Federation", "South Africa", 
                      "Korea, Rep. of", "Turkey", "United Kingdom", 
                      "United States")) %>%
  mutate(COUNTRY = recode(COUNTRY,
                          "Russian Federation" = "Russia",
                          "Korea, Rep. of" = "South Korea")) %>%
  mutate(year = as.numeric(year))  %>%
  mutate(china_imports = as.double(china_imports))

china_imf_trade <- 
  read_excel("Exports_China.xlsx", skip = 5) %>%
  pivot_longer(cols = - c(`...1`),
               names_to = "year") %>%
  rename(COUNTRY = `...1`, china_exports = value) %>%
   filter(COUNTRY %in% c("Argentina", "Australia", "Brazil", "Canada", "France",
                      "Germany", "India", "Indonesia", "Italy", "Japan",
                      "Mexico", "Russian Federation", "South Africa", 
                      "Korea, Rep. of", "Turkey", "United Kingdom", 
                      "United States")) %>%
  mutate(COUNTRY = recode(COUNTRY,
                          "Russian Federation" = "Russia",
                          "Korea, Rep. of" = "South Korea")) %>%
  mutate(year = as.numeric(year),
         china_exports = as.double(china_exports)) %>%
  filter(year >= 2009) %>%
  left_join(g20_gdp, by = c("year", "COUNTRY")) %>%
  left_join(china_imf_imports, by = c("year", "COUNTRY")) %>%
  mutate(total_trade = china_exports + china_imports) %>%
  mutate(china_export_prop = china_exports/gdp_tot) %>%
  mutate(china_import_prop = china_imports/gdp_tot) %>%
  mutate(trade_flow_prop = total_trade/gdp_tot)

pew <- 
  bind_rows(pew_2019, pew_2018, pew_2017, pew_2016, pew_2015, pew_2014,
            pew_2013, pew_2012, pew_2011, pew_2010, pew_2009)  %>%
  left_join(china_imf_trade, by = c("year", "COUNTRY")) %>%
  group_by(COUNTRY) %>%
  mutate(fav_china_scale = case_when(fav_China == "Very unfavorable" ~ 1,
                                     fav_China == "Somewhat unfavorable" ~ 2,
                                     fav_China == "Somewhat favorable" ~ 3,
                                     fav_China == "Very favorable" ~ 4,
                                     TRUE ~ NA_real_))
```


```{r}
set.seed(10)
basic_model <- stan_glm(data = pew,
         formula = fav_china_scale ~ trade_flow_prop,
         refresh = 0)

print(basic_model, digits = 4)

tbl_regression(basic_model, intercept = TRUE) %>%
  as_gt() %>%
  tab_header(title = "Regression of Global Attitudes Torwards China",
             subtitle = "The Effect of Total Trade Flow on Favorability 
             Towards China (1 = Very unfavorable, 4 = Very favorable)") %>%
  tab_source_note(md("Pew Global Attidues & Trends Survey (2009-2019), 
                     IMF World Trade Flows (2009-2019),
                     World Bank G20 GDPs (2019-2019)"))


basic_model %>% 
  as_tibble() %>% 
  rename(mu = `(Intercept)`) %>%
  ggplot(aes(x = mu)) +
    geom_histogram(aes(y = after_stat(count/sum(count))),
                   fill = "lightblue4", 
                   color = "gray97",
                   bins = 100) +
    labs(title = "Posterior Probability Distribution of Global Attitudes
         Towards China",
         subtitle = "The Effect of Total Trade Flow on Favorability 
             Towards China (1 = Very unfavorable, 4 = Very favorable)",
         x = "Attitudes Towards China",
         y = "Probability") +
    theme_classic()

```

fav_china_scale ~ gdp_share






```{r}

cc_2019 <- read_sav("2019 Chicago Council Survey - Datafile.sav")

glimpse(pew_2019)

pew_2019_c <- pew_2019 %>%
  filter(country == "United States") %>%
  ggplot(aes(x = FAV_CHINA)) +
  geom_bar()
```

